Einstein's gravity from a polynomial affine model

### 2015-10-20 AffGR-PRD.tex
Starting new update counting

\DeclareDocumentCommand{\Ff}{ o }{ \IfValueTF{#1}{ F_{(#1)} }{ F } }

@@

The Eq.~\eqref{SimpleEOM} is related through the second Bianchi identity to the harmonic curvature condition~\cite{bourguignon1981varietes},
\begin{equation}
  \label{harm-curv}
  \nabla_\lambda R_{\mu\nu}{}^\lambda{}_\rho = 0,
\end{equation}
and it can be shown that a manifold with harmonic curvature is equivalent (in four dimensions) to a manifold with harmonic Weyl tensor~\cite{Berger:1969} and constant scalar curvature, or in other words the Ricci tensor is a Codazzi tensor~\footnote{A Codazzi tensor is a symmetric $(0,2)$-type tensor, $T$, satisfying the condition \mbox{$D_X T(Y,Z) = D_Y T(X,Z)$~\cite{Derdzinski01071983}.}}. For prove of these equivalences, see Refs.~\cite{Derdzinski:1985,Besse}.

Equations.~\eqref{SimpleEOM} and~\eqref{harm-curv} are geometrically equivalent to the 
Interestingly, the Eq.~\eqref{SimpleEOM} can be obtained from an effective gravitational Yang--Mills functional action~\cite{stephenson1958quadratic,kilmister1961use,Yang1974},
\begin{equation}
  S_{\textsc{ym}} = \int \Tr \left( \Rif{}{} \we \st \Rif{}{} \right),
\end{equation}
where $\Rif{}{} \in \Omega^2(\Mi, T^*\Mi \otimes T\Mi)$ is the curvature two-form, the operator $\st$ denotes the Hodge star, and the trace is taken on the bundle indices (see Ref.~\cite{bourguignon1982yang}). Albeit this effective theory has been widely studied, it has been considered as a model for a metric field instead of a theory for the connection. Therefore, within the formalism of Palatini, besides Eq.~\eqref{SimpleEOM} an extra field equation appears (for the vielbein field), which strongly constraints the solutions of the gravitational Yang--Mills~\footnote{We thank J.~Zanelli for sharing his personal communications with C.~N.~Yang, and clarify this aspect of the effective model.}. Intriguingly, this effective theory is not renormalizable ---according to the arguments in Refs.~\cite{McGady:2013sga,Camanho:2014apa}---, although it has been discussed in Ref.~\cite{Chen:2010at} that at least the ghost problem can be avoided through the arguments exposed in Refs.~\cite{Kleinert:1987eb,Bender:2007wu,Bender:2008vh,Mannheim:2009zj}.

>>>>

%% \DeclareDocumentCommand{\Ff}{ o }{ \IfValueTF{#1}{ F_{(#1)} }{ F } }
\DeclareDocumentCommand{\Ff}{ s o }{ \IfBooleanTF{#1}
    { \IfValueTF{#2}{ \boldsymbol{F}_{(#2)} }{ \boldsymbol{F} } }
    { \IfValueTF{#2}{            {F}_{(#2)} }{            {F} } } }

@@

The Eq.~\eqref{SimpleEOM} is related through the second Bianchi identity to the harmonic curvature condition~\cite{bourguignon1981varietes},
\begin{equation}
  \label{harm-curv}
  \nabla_\lambda R_{\mu\nu}{}^\lambda{}_\rho = 0,
\end{equation}
and it can be shown that a manifold with harmonic curvature is equivalent (in four dimensions) to a manifold with harmonic Weyl tensor and constant scalar curvature~\cite{Berger:1969}, or in other words the Ricci tensor is a Codazzi tensor~\footnote{A Codazzi tensor is a symmetric $(0,2)$-type tensor, $T$, satisfying the condition \mbox{$D_X T(Y,Z) = D_Y T(X,Z)$~\cite{Derdzinski01071983}.}}. For prove of these equivalences, see Refs.~\cite{Derdzinski:1985,Besse}.

%% Equations~\eqref{SimpleEOM} and~\eqref{harm-curv} are geometrically equivalent to the 
Notice that Eqs.~\eqref{SimpleEOM} and~\eqref{harm-curv} accept a geometrical interpretation equivalent to that of the field equations of a pure Yang--Mills theory, which in the language of differential forms are
\begin{align}
  \df \Ff*[2] &= 0, & \df \st \Ff*[2] &= 0,
\end{align}
where $\Ff*[2]$ is the field strength 2-form (the curvature 2-form of the connection in the principal bundle), and the operator $\st$ denotes the Hodge star. Now, these Yang--Mills field equations are obtained from the well-known action functional
\begin{equation}
  S_{\textsc{ym}} = \int \Tr \Big( \Ff*[2] \st \Ff*[2] \Big).
\end{equation}

Interestingly, the Eq.~\eqref{SimpleEOM} ---equivalently Eq.~\eqref{harm-curv}--- can be obtained from an effective gravitational Yang--Mills functional action~\cite{stephenson1958quadratic,kilmister1961use,Yang1974}, %constructed as the trace of the 
\begin{equation}
  \label{SKY}
  S_{\textsc{ym}} = \int \Tr \left( \Rif{}{} \st \Rif{}{} \right) = \int \left( \Rif{a}{b} \st \Rif{b}{a} \right),
\end{equation}
where $\Rif{}{} \in \Omega^2(\Mi, T^*\Mi \otimes T\Mi)$ is the curvature two-form, the operator $\st$ denotes the Hodge star, and the trace is taken on the bundle indices (see Ref.~\cite{bourguignon1982yang}).

The gravitational model described by the action in Eq.~\eqref{SKY} is called Stephenson--Kilmister--Yang (or SKY for short). However, the standard interpretation of this model requires a metric tensor. Therefore, a quick analysis of the field equations \`a la Palatini shows that the field equation

%% \documentclass[aps,prd,12pt,twocolumn,superscriptaddress,showpacs,showkeys,reprint]{revtex4-1}

%% \usepackage{amsmath,amsthm,latexsym,amssymb,amsfonts}
%% \usepackage{xcolor}
%% \usepackage[%
%%   colorlinks=true,
%%   urlcolor=blue,
%%   linkcolor=blue,
%%   citecolor=blue
%% ]{hyperref}
%% \usepackage{etoolbox}
%% \usepackage{breqn}

%% \makeatletter
%% \let\cat@comma@active\@empty
%% \makeatother

%% %------------------
%% %--------- Definitions
%% %------------------
%% %% \input{Def-article.tex}
%% \usepackage{mathtools,amsmath,amssymb,amsfonts,dsfont,mathrsfs,amsthm}
%% \usepackage{graphicx}
%% \usepackage{centernot}
%% %% \usepackage{hyperref}
%% \usepackage{xcolor}
%% \usepackage{comment}
%% %% \hypersetup{linktocpage,colorlinks=true,urlcolor=blue!80!red,linkcolor=blue,citecolor=red}
%% %\usepackage{feynmf}
%% \usepackage{siunitx}
%% \usepackage{array}
%% %% \usepackage{ulem}
%% %\usepackage{tikz}
%% \usepackage{braket}
%% \usepackage{xparse}

%% %-------------------------------Theorems
%% \newtheorem{Def}{Definition}[section]
%% \newtheorem{Thm}[Def]{Theorem}
%% \newtheorem{Lem}[Def]{Lemma}
%% \newtheorem{Pos}[Def]{Postulate}
%% \newtheorem{Exa}[Def]{Example}
%% \newtheorem{Cor}[Def]{Corrolary}
%% \newtheorem{Pro}[Def]{Proposition}

%% %---------------------------------New commands
%% \newcommand{\A}{\mathcal{A}} %% This is equivalent to \Ag (no args)
%% \newcommand{\abs}[1]{\left|{#1}\right|}
%% \DeclareMathOperator{\ad}{ad}
%% \DeclareMathOperator{\Ad}{Ad}
%% \DeclareDocumentCommand{\Ag}{ s o }{ \IfBooleanTF{#1}
%%     { \IfValueTF{#2}{ \boldsymbol{\mathcal{A}}_{(#2)} }{ \boldsymbol{\mathcal{A}} } }
%%     { \IfValueTF{#2}{            {\mathcal{A}}_{(#2)} }{            {\mathcal{A}} } } }
%% %% \newcommand{\Ag}{\mathcal{A}_{(1)}}
%% %% \newcommand{\Agf}{\boldsymbol{\mathcal{A}}}
%% \DeclareDocumentCommand{\Af}{ s o }{ \IfBooleanTF{#1}
%%     { \IfValueTF{#2}{ \boldsymbol{A}_{(#2)} }{ \boldsymbol{A} } }
%%     { \IfValueTF{#2}{            {A}_{(#2)} }{            {A} } } }
%% %% \newcommand{\Af}{ {\mathbf{A}} }
%% %% \newcommand{\AF}[1]{ {\mathbf{A}}_{({#1})} }
%% \newcommand{\hAf}{ \hat{\mathbf{A}}_{(1)} }
%% \newcommand{\hAF}[1]{ \hat{\mathbf{A}}_{(#1)} }
%% \newcommand{\bboxed}[1]{{\color{red}{\boxed{\boxed{\textcolor{black}{#1}}}}}}
%% \newcommand{\C}{\mathbb{C}}
%% \newcommand{\Cl}{\mathcal{C}\!\ell}
%% \newcommand{\cdf}[1][]{{\boldsymbol{\mathcal{D}}}{#1}\!}
%% \newcommand{\covd}{\mathcal{D}}
%% \newcommand{\D}{\mathscr{D}}
%% \newcommand{\df}[1][]{\mathbf{d}{#1}}
%% \newcommand{\dfd}{{\mathbf{d}}^\dag\!}
%% \newcommand\ded{\mathrm{d}^\dag}
%% \DeclareMathOperator{\End}{End}
%% \newcommand{\ele}[2][]{\frac{d}{dt}\left(\frac{\partial\mathcal{L}}{\partial \dot{#2}^{#1}}\right) - \frac{\partial\mathcal{L}}{\partial {#2}^{#1}}}
%% \newcommand{\fele}[2][]{\partial_\mu \left(\frac{\delta\mathcal{L}}{\delta\left(\partial_\mu{#2}^{#1}\right)}\right) - \frac{\delta\mathcal{L}}{\delta {#2}^{#1}}}
%% \newcommand{\vb}[1]{\vec{e}_{#1}}
%% %% \newcommand{\fb}[1]{\widetilde{e}{}^{ #1}}
%% \newcommand\fder[3][]{\frac{\delta^{#1}{#2}}{\delta {#3}^{#1}}}
%% \newcommand\fdern[4][]{\frac{\delta^{#1}{#2}}{\delta {#3} \cdots \delta {#4}}}
%% %% \newcommand{\Fc}{\mathcal{F}}
%% %% \newcommand{\F}{\boldsymbol{\mathcal{F}}}
%% %% \newcommand{\Fg}{\boldsymbol{\mathcal{F}}_{(2)}}
%% \DeclareDocumentCommand{\Fg}{ s o }{ \IfBooleanTF{#1}
%%     { \IfValueTF{#2}{ \boldsymbol{\mathcal{F}}_{(#2)} }{ \boldsymbol{\mathcal{F}} } }
%%     { \IfValueTF{#2}{            {\mathcal{F}}_{(#2)} }{            {\mathcal{F}} } } }
%% %% \newcommand{\Ff}{{\mathbf{F}}}
%% %% \DeclareDocumentCommand{\Ff}{ o }{ \IfValueTF{#1}{ F_{(#1)} }{ F } }
%% \DeclareDocumentCommand{\Ff}{ s o }{ \IfBooleanTF{#1}
%%     { \IfValueTF{#2}{ \boldsymbol{F}_{(#2)} }{ \boldsymbol{F} } }
%%     { \IfValueTF{#2}{            {F}_{(#2)} }{            {F} } } }
%% \newcommand{\FF}[1]{{\mathbf{F}}_{(#1)}}
%% \newcommand{\hFF}[1]{{\mathbf{\hat{F}}}_{(#1)}}
%% \newcommand{\fy}{\centernot}
%% \newcommand{\G}{\mathscr{G}}
%% \newcommand{\ga}{\gamma}
%% \newcommand{\gf}{\boldsymbol{\gamma}}
%% \newcommand{\Ga}{\Gamma}
%% \newcommand{\conn}[3]{\left(\Gamma_{#1}\right)^{#2}{}_{#3}}
%% \newcommand{\connn}[3]{\Gamma_{#1}{}^{#2}{}_{#3}}
%% \newcommand{\hcon}[3]{\hat{\Gamma}_{#1}{}^{#2}{}_{#3}}
%% \newcommand{\Ha}{\mathscr{H}}
%% \newcommand{\He}{\mathbb{H}}
%% \newcommand{\Hi}{\mathcal{H}}
%% \newcommand{\Hint}{\underline{\sc Hint:} }
%% \DeclareMathOperator{\hs}{\star\!\!}
%% \DeclareMathOperator{\st}{\star}
%% \newcommand{\J}{\mathscr{J}}
%% \newcommand{\K}{\mathbb{K}}
%% \newcommand{\KK}{Kaluza-Klein\ }
%% \newcommand{\Lag}{\mathscr{L}}
%% \newcommand{\Li}{\mathcal{L}}
%% \newcommand{\La}[1][]{\triangle_{#1}}
%% \newcommand{\Lap}{\nabla^2}
%% \newcommand{\lr}[1]{\stackrel{\leftrightarrow}{#1}}
%% \newcommand{\M}{\ensuremath{\mathscr{M}}}
%% \DeclareMathOperator{\Mat}{Mat}
%% \newcommand{\Mi}{\mathcal{M}}
%% \newcommand{\MN}{Maldacena-N\'u\~nez\ }
%% \newcommand{\N}{\ensuremath{\mathscr{N}}}
%% \newcommand{\Na}{\mathbb{N}}
%% \newcommand{\No}{\mathcal{N}}
%% \newcommand{\norm}[1]{\left\|#1\right\|}
%% \newcommand{\Op}{\mathcal{O}}
%% \newcommand{\Or}{\mathscr{O}}
%% \newcommand\pder[3][]{\frac{\partial^{#1}{#2}}{\partial {#3}^{#1}}}
%% \newcommand\pdern[4][]{\frac{\partial^{#1}#2}{\partial #3\cdots\partial #4}}
%% \DeclareMathOperator{\Pfaff}{Pfaff}
%% \newcommand{\Qh}[1][]{\ensuremath{\hat{Q}_{#1}}}
%% \newcommand{\R}{\mathbb{R}}
%% \newcommand{\Ri}{\mathcal{R}}
%% %% \newcommand{\S}{\mathscr{S}}
%% \newcommand{\SM}{Standard Model {}}%\mathscr{S}}
%% \DeclareDocumentCommand\Te{o o m }{\mathcal{T}{}^{#1}_{#2}(#3)}
%% \newcommand{\T}{\mathscr{T}}
%% \newcommand{\tor}{\mathcal{T}}
%% \newcommand{\tors}[3]{\mathcal{T}{}_{#1}{}^{#2}{}_{#3}}
%% \newcommand{\torss}[3]{T_{#1}{}^{#2}{}_{#3}}
%% \newcommand\vdj[1]{\left< \Delta J \right>_{#1}}
%% \newcommand{\w}{{\scriptstyle\wedge}\!}
%% \newcommand{\we}{{\scriptstyle\wedge}}
%% \newcommand{\Z}{\mathbb{Z}}

%% \newcommand{\dbar}[1]{\ensuremath{\mathchar'26\mkern-12mu \mathrm{d}^{#1}}\!}

%% %--------------------------- New Greek
%% \newcommand{\tht}{\ensuremath{\theta}}
%% \newcommand{\bet}{\ensuremath{\bar{\eta}}}
%% \newcommand{\bps}{\ensuremath{\bar{\psi}}}
%% \newcommand{\bc}{\ensuremath{\bar{\chi}}}
%% \newcommand{\Bps}{\ensuremath{\bar{\Psi}}}
%% \newcommand{\Bx}{\ensuremath{\bar{\Xi}}}
%% \newcommand{\bph}{\ensuremath{\bar{\phi}}}
%% \newcommand{\vph}{\ensuremath{\varphi}}
%% \newcommand{\bvph}{\ensuremath{\bar{\varphi}}}
%% \newcommand{\bth}{\ensuremath{\bar{\theta}}}
%% \newcommand{\hph}{\ensuremath{\hat{\phi}}}

%% \newcommand{\bs}[1]{\boldsymbol{#1}}

%% \renewcommand{\div}{{\mathbf{div}}}
%% \newcommand{\grad}{{\mathbf{grad}}}
%% \newcommand{\curl}{{\mathbf{curl}}}

%% \newcommand\VI[2]{\hat{e}^{\hat{#1}}_{\hat{#2}}}
%% \newcommand\VIF[1]{\hat{\boldsymbol{e}}^{\hat{#1}}}
%% \newcommand\VIN[2]{\hat{E}^{\hat{#1}}_{\hat{#2}}}
%% \newcommand\VINF[1]{\hat{\boldsymbol{E}}_{\hat{#1}}}
%% \newcommand\hvi[2]{\hat{e}^{{#1}}_{{#2}}}
%% \newcommand\hvin[2]{\hat{E}^{{#1}}_{{#2}}}
%% \newcommand\hvif[1]{\hat{\boldsymbol{e}}^{{#1}}}
%% \newcommand\hvinf[1]{\hat{\boldsymbol{E}}_{{#1}}}
%% \newcommand\vi[2]{e^{{#1}}_{{#2}}}
%% \newcommand\vin[2]{E^{{#1}}_{{#2}}}
%% \newcommand\vif[1]{\boldsymbol{e}^{{#1}}}
%% \newcommand\vinf[1]{\boldsymbol{E}_{{#1}}}
%% %% \newcommand\Vi[2]{e^{\hat{#1}}_{\hat{#2}}}
%% %% \newcommand\Vin[2]{E^{\hat{#1}}_{\hat{#2}}}
%% \newcommand\GAM[1]{{\gamma}^{\hat{#1}}}
%% %% \newcommand\Gam[1]{\gamma^{\hat{#1}}} 
%% \newcommand\gam[1]{\gamma^{{#1}}}
%% \newcommand\hgam[1]{\hat{\gamma}^{{#1}}}
%% \newcommand\NAB[1]{\hat{\nabla}_{\hat{#1}}}
%% \newcommand\Nab[1]{\nabla_{\hat{#1}}}
%% \newcommand\nab[1]{\nabla_{{#1}}}
%% \newcommand\PA[1]{\partial_{\hat{#1}}}
%% \newcommand\pa[1]{\partial_{{#1}}}
%% \newcommand\PAU[1]{\partial^{\hat{#1}}}
%% \newcommand\pau[1]{\partial^{{#1}}}
%% \newcommand\lf[1]{{\omega}^{{#1}}}
%% \newcommand\lft[1]{\hat{\omega}^{{#1}}}
%% \newcommand\SPI[1]{\hat{\omega}_{\hat{#1}}}
%% \newcommand\SPIF[2]{\hat{\boldsymbol{\omega}}^{\hat{#1}}{}_{\hat{#2}}}
%% %% \newcommand\Spi[1]{\omega_{\hat{#1}}}
%% \newcommand\spi[1]{\omega_{{#1}}}
%% \newcommand\tspi[1]{\tilde{\omega}_{{#1}}}
%% \newcommand\spif[2]{{\boldsymbol{\omega}}^{{#1}}{}_{{#2}}}
%% \newcommand\tspif[2]{{\tilde{\boldsymbol{\omega}}}^{{#1}}{}_{{#2}}}
%% \newcommand\hspi[1]{\hat{\omega}_{{#1}}}
%% \newcommand\hspif[2]{\hat{\boldsymbol{\omega}}^{{#1}}{}_{{#2}}}
%% %%%%%%%%% Beware of the inconsistency between
%% %%%%%%%%% \Rif and \RIF
%% \newcommand{\RIF}[2]{\hat{\boldsymbol{\mathcal{R}}}^{\hat{#1}}{}_{\hat{#2}}}
%% \newcommand{\hRif}[2]{\hat{\boldsymbol{\mathcal{R}}}^{{#1}}{}_{{#2}}}
%% \newcommand{\Rif}[2]{\boldsymbol{\mathcal{R}}^{{#1}}{}_{{#2}}}
%% \newcommand{\tRif}[2]{\tilde{\boldsymbol{\mathcal{R}}}^{{#1}}{}_{{#2}}}
%% \newcommand{\Tf}[1]{\boldsymbol{\mathcal{T}}^{#1}}
%% \newcommand{\hTf}[1]{\hat{\boldsymbol{\mathcal{T}}}^{#1}}
%% \newcommand{\TF}[1]{\hat{\boldsymbol{\mathcal{T}}}^{\hat{#1}}}
%% \newcommand{\Tor}[2]{\mathcal{T}^{#1}{}_{#2}}
%% \newcommand{\cont}[3]{\mathcal{K}_{#1}{}^{#2}{}_{#3}}
%% \newcommand{\contf}[2]{\boldsymbol{\mathcal{K}}^{#1}{}_{#2}}
%% \newcommand{\hcont}[3]{\hat{\mathcal{K}}_{#1}{}^{#2}{}_{#3}}
%% \newcommand{\hcontf}[2]{\hat{\boldsymbol{\mathcal{K}}}^{#1}{}_{#2}}
%% \newcommand{\CONT}[3]{\hat{\mathcal{K}}_{\hat{#1}}{}^{\hat{#2}}{}_{\hat{#3}}}
%% \newcommand{\CONTF}[2]{\hat{\boldsymbol{\mathcal{K}}}^{\hat{#1}}{}_{\hat{#2}}}

%% %% \newcommand{\ket}[1]{\left.\left|#1\right.\right>}
%% %% \newcommand{\bra}[1]{\left.\left<#1\right.\right|}
%% \renewcommand\bra[1]{\Bra{#1}}
%% \renewcommand\ket[1]{\Ket{#1}}
%% \newcommand{\bkt}[3]{\Braket{ {#1} | {#2} | {#3} } }
%% \newcommand{\bk}[2]{\Braket{ {#1} | {#2} } }
%% \newcommand{\comm}[2]{\left[#1,#2\right]}
%% \newcommand{\acomm}[2]{\left\{#1,#2\right\}}
%% \newcommand{\vev}[1]{\ensuremath{\left<#1\right>}}
%% \renewcommand{\set}[1]{\ensuremath{\Set{ #1 }}}

%% \newcommand{\relphantom}[1]{\mathrel{\phantom{#1}}}

%% \newcommand{\Ric}{\operatorname{Ric}}
%% \newcommand*{\diag}{\operatorname{diag}}
%% \newcommand{\id}{\operatorname{id}}
%% \newcommand{\tr}{\operatorname{tr}}
%% \newcommand{\Tr}{\operatorname{Tr}}
%% \newcommand{\Ker}{\operatorname{Ker}}
%% \renewcommand{\Im}{\operatorname{Im}}
%% \newcommand{\sgn}{\operatorname{sgn}}
%% \newcommand{\Ln}{\operatorname{Ln}}
%% \newcommand{\Ei}{\operatorname{Ei}}
%% \newcommand{\csch}{\operatorname{csch}}
%% \newcommand{\arcsinh}{\operatorname{arcsinh}}
%% \DeclareMathOperator\Br{Br}

%% \newcommand{\beq}{\begin{equation}}
%% \newcommand{\eeq}{\end{equation}}
%% \newcommand{\ber}{\begin{eqnarray}}
%% \newcommand{\eer}{\end{eqnarray}}

%% \renewcommand{\(}{\left(}
%% \renewcommand{\)}{\right)}
%% \renewcommand{\[}{\left[}
%% \renewcommand{\]}{\right]}

%% \newcommand{\uf}[2][]{\ensuremath{u_{#1}\(\vec{#2}\)}}
%% \newcommand{\ufb}[2][]{\ensuremath{\bar{u}_{#1}\(\vec{#2}\)}}
%% \newcommand{\vf}[2][]{\ensuremath{v_{#1}\(\vec{#2}\)}}
%% \newcommand{\vfb}[2][]{\ensuremath{\bar{v}_{#1}\(\vec{#2}\)}}
%% \newcommand\pol[2][]{\ensuremath{\varepsilon_{#1}(\vec{#2})}}
%% \newcommand\polc[2][]{\ensuremath{\varepsilon^*_{#1}(\vec{#2})}}
%% \newcommand{\ann}[3]{\ensuremath{#1\(\vec{#2},#3\)}}
%% \newcommand{\cre}[3]{\ensuremath{#1^\dag\(\vec{#2},#3\)}}
%% %% \newcommand{\uf}[2]{\ensuremath{u\(\vec{#1},#2\)}}
%% %% \newcommand{\ufb}[2]{\ensuremath{\bar{u}\(\vec{#1},#2\)}}
%% %% \newcommand{\vf}[2]{\ensuremath{v\(\vec{#1},#2\)}}
%% %% \newcommand{\vfb}[2]{\ensuremath{\bar{v}\(\vec{#1},#2\)}}
%% %% \newcommand{\ann}[3]{\ensuremath{#1\(\vec{#2},#3\)}}
%% %% \newcommand{\cre}[3]{\ensuremath{#1^\dag\(\vec{#2},#3\)}}

%% \newcommand{\dif}{{\mathrm{d}}}
%% \newcommand{\difn}[1]{{\mathrm{d}}^{#1}}
%% \newcommand{\dn}[2]{{\mathrm{d}}^{#1}{#2}\;}
%% \newcommand{\dbarn}[2]{\dbar{#1}{#2}\;}
%% \newcommand*{\de}[1]{\mathop{\mathrm{d}#1}\nolimits}% differential, facultative argoment between square parentheses
%% \newcommand*{\desec}[1][]{\mathop{\mathrm{d^2}#1}\nolimits}% second differential, facultative argoment between square parentheses
%% \newcommand{\der}[2]{\frac{\de{#1}}{\de{#2}}}% first derivative 
%% %\newcommand{\pder}[2]{\frac{\pa{}#1}{\pa{}{#2}}}% first derivative 
%% \newcommand{\inlineder}[2]{\mathrm{d}{#1}/\mathrm{d}{#2}}% in-line first derivative
%% \newcommand{\dersec}[2]{\frac{{\desec[#1]}}{\de[{#2}^2]}}% second derivative
%% %% \newcommand{\dx}{\de[x]}% frequently used differentials
%% %% \newcommand{\dy}{\de[y]}
%% %\newcommand{\df}{\de[f]}

%% %------------------
%% %--------- Format
%% %------------------
%% \newcommand{\out}[1]{{\color{red} {#1}}}
%% \newcommand{\pro}[1]{{\color{blue!70!black} {#1}}}
%% \newcommand{\hl}[1]{{\color{red} \bfseries{#1}}}

%% \newcommand\UTFSM{Departamento de F\'\i sica, Universidad T\'{e}cnica Federico Santa Mar\'\i a, \\ Casilla 110-V, Valpara\'\i so, Chile}
%% \newcommand\CCTVal{Centro Cient\'\i fico Tecnol\'ogico de Valpara\'\i so, \\ Casilla 110-V, Valpara\'\i so, Chile}
%% \newcommand\CFF{Centro de F\'\i sica Fundamental,  Universidad de los Andes,\\ 5101 M\'erida, Venezuela}

%% \hypersetup{%
%%   pdftitle={Einstein's gravity from a polynomial affine model},
%%   pdfauthor={Oscar Castillo-Felisola,}{Aureliano Skirzewski},
%%   pdfkeywords={Affine Gravity,} {Torsion,} {Generalised Gravity.},
%%   pdflang={English}
%% }

%% %------------------
%% %--------- Document
%% %------------------
%% \begin{document}

%% \title{Einstein's gravity from a polynomial affine model}

%% \author{Oscar \surname{Castillo-Felisola}}
%% \email{o.castillo.felisola@gmail.com}
%% \affiliation{\CCTVal.}
%% \affiliation{\UTFSM.}

%% \author{Aureliano \surname{Skirzewski}}
%% \email{askirz@gmail.com}
%% \affiliation{\CFF.}

%% %% --------- Abstract
%% \begin{abstract}
%%   We show that the effective field equations for a recently formulated polynomial affine model of gravity, in the sector of a torsion-free connection, accept general Einstein manifolds ---with or without cosmological constant--- as solutions. Moreover, these effective field equations coincide with those obtained from a gravitational Yang--Mills theory known as Stephenson--Kilmister--Yang theory. Additionally, we find a generalization of a minimally coupled massless scalar field in General Relativity with a ``minimally'' coupled scalar field in this affine model.
%% \end{abstract}

%% \pacs{02.40.Ma,04.50.Kd,04.90.+e}
%% \keywords{Affine Gravity, Torsion, Generalized Gravity.}

%% \maketitle

%% \section{\label{intro}Introduction}

%% Classically, General Relativity is the most successful theory of gravitational interactions. However, it is believed to be the effective theory of a, yet to be discovered, more fundamental one. Among the problems of General Relativity we mention a few aspects related with the quantization: First, the fact that in the standard formalism of quantization General Relativity is non-renormalizable~\cite{'tHooft:1973us,'tHooft:1974bx,Deser:1974cz,Deser:1974cy}. Second, the Wheeler--DeWitt equations are not well-defined in general due to their nonpolynomial dependence on the Arnowitt--Deser--Misner (or ADM) variables~\cite{Arnowitt:1959ah,Arnowitt:1960es,WheelerGeo,DeWitt:1967yk,DeWitt:1967ub,DeWitt:1967uc}. One of the most successful quantization methods of gravitational interactions ---developed from ideas by Gambini and Trias~\cite{Gambini:1980yz,Gambini:1986ew}, and Ashtekar~\cite{Ashtekar:1986yd,Ashtekar:1987gu}---, hints that General Relativity is not as complete as expected, since the Lagrangian formulation includes (at least) an extra term known as Holst term~\cite{Holst:1995pc}. On the other hand, it is well known that in the standard formulation of General Relativity the skew-symmetric part of the connection (or torsion) is assumed to be zero, albeit it is known that such assumption can be relaxed once matter is added, in particular fermionic matter~\cite{Kibble:1961ba}.

%% Standing on the argument of the necessity of a quantum theory of gravity, several generalizations of Einstein's General Relativity have been proposed. One important class of these generalizations considers the connection field to be independent of the metric, known as Palatini type theories. Within this class of theories one finds the generalization due to Cartan, which considers a connection with nonvanishing torsion~\cite{Cartan1922,Cartan1923,Cartan1924,Cartan1925}. Interestingly, gravitational theories with generic linear connections have degrees of freedom which do not correspond to the expected massless graviton~\cite{Sezgin:1979zf}. Albeit these gravitational theories with an arbitrary connection possess ghosts, there are examples of well-behaved (stable) systems which have ghosts, such are the cases of the Pais--Uhlenbeck oscillator~\cite{Mannheim:2004qz,Bender:2007wu,Smilga:2008pr,Ilhan:2013xe} or the higher derivative supersymmetric quantum mechanical system presented in Ref.~\cite{Robert:2008}.

%% Therefore, under the premises of incompleteness and non-polynomial structure of the theory, 
%% %%%%%%%%% THE MODEL %%%%%%%%%
%% in a previous paper~\cite{Skirzewski:2014eta}, we presented a polynomial (purely) affine gravitational model in four dimensions built up entirely on the basis of full diffeomorphism invariance, and restricting ourselves to consider only naive power-counting renormalizable terms (which by no means guarantees the renormalizability of the system). We showed that its non-relativistic limit around a homogeneous and isotropic spacetime yields a Newtonian gravitational potential, despite the existence of torsion. We also highlighted the possibility of using standard methods to quantize the model, due to its polynomial structure (unlike the earliest proposals~\cite{Eddington1923math,schrodinger1950space}), and also the likelihood of avoiding the uniqueness of diffeomorphism-invariant states from Loop Quantum Gravity programme~\cite{Lewandowski:2005jk}, due to the absence of a fundamental metric, or in other words, the absence of flux operators.

%% Interestingly, by construction, the polynomial affine gravity proposed in Ref.~\cite{Skirzewski:2014eta} has no explicit terms leading to three-point graviton vertices, since all graviton self-interaction is mediated by the torsion. This characteristic might allow to bypass the general postulates supporting the no-go theorems stated in Refs.~\cite{McGady:2013sga,Camanho:2014apa}, where it is proved that generic three-point graviton interactions are highly constrained by causality and analyticity of the $S$-matrix, and the only \emph{acceptable} structure of the three-point graviton vertices is the one coming from General Relativity.
%% %%Additionally, it is well known that the three-point graviton vertices lead to non-renormalizability of a theory ---in a model independent way---~\cite{McGady:2013sga,Camanho:2014apa}. However, in the considered framework all graviton self-interaction is mediated by the torsion, which might allow to bypass the general postulates supporting the theorem.

%% The aim of this work is to show that in the vanishing torsion sector, the field equations of the polynomial affine gravity are a generalization of the Einstein's equations. % in vacuum. In addition, we show that ---in the same sector--- under the assumption of the existence of a unique non-degenerated, covariantly constant $\binom{0}{2}$-tensor, $g$ (which could be thought as a metric), the system of a scalar field coupled with the polynomial affine gravity accepts the minimally coupled Einstein--Klein--Gordon as a solution.
%% The paper is organized as follows. In Sec.~\ref{model}, we present briefly the polynomial affine gravity model, and summarize the results obtained in Ref.~\cite{Skirzewski:2014eta} concerning the Newtonian limit of the model. In Sec.~\ref{rlimit}, we restrict ourselves to the sector of the theory with vanishing torsion, and find the field equations; which surprisingly are a known generalization of the Einstein's field equation. Then, in Sec.~\ref{matter} we show that under certain considerations the coupling of the gravitational model with a scalar field represents a generalization of the minimally coupled system Einstein--Klein--Gordon. Finally, in Sec.~\ref{conclusions} we summarize and discuss the possible implications of the results.

%% \section{\label{model}Polynomial affine gravity}

%% First of all, we highlight that the model constructed below has as fundamental field an affine connection, and no metric fields is needed for neither contracting nor lowering or raising indices. Moreover, in order to guarantee the correct transformation of the Lagrangian density, the geometrical objects used to write down the action will be the curvature and torsion of an affine connection, $\hat{\Gamma}^\mu{}_{\rho\sigma}$, which accepts a decomposition on irreducible components as
%% \begin{equation}
%%   \hat{\Gamma}^\mu{}_{\rho\sigma} = {\Gamma}^\mu{}_{\rho\sigma} + T^\mu{}_{\rho\sigma} = {\Gamma}^\mu{}_{\rho\sigma} + \epsilon_{\rho\sigma\lambda\kappa}T^{\mu,\lambda\kappa}+A_{[\rho}\delta^\mu_{\nu]},
%% \end{equation}
%% where ${\Gamma}^\mu{}_{\rho\sigma}$ is symmetric in the lower indices, $A_\mu$ is a vector field corresponding to the trace of torsion, and  $T^{\mu,\lambda\kappa}$ is a Curtright field~\cite{Curtright:1980yk}, satisfying \mbox{$T^{\kappa,\mu\nu } = - T^{\kappa,\nu\mu }$} and $\epsilon_{\lambda\kappa\mu\nu}T^{\kappa,\mu\nu }=0$. Since no metric is present  the epsilon symbols are not related by raising (lowering) their indices, but instead we demand that \mbox{$\epsilon^{\delta\eta\lambda\kappa}\epsilon_{\mu\nu\rho\sigma}=4!\delta^{\delta}{}_{[\mu}\delta^\eta{}_{\nu}\delta^{\lambda}{}_{\rho} \delta^\kappa{}_{\sigma]}$.}
%% \begin{widetext}
%% Using the above decomposition, the most general (power-counting renormalizable) action preserving diffeomorphisms is~\footnote{We have dropped all terms which can be related to those in Eq.~\eqref{4dfull} through a boundary term.}
%%   \begin{dmath}
%%     \label{4dfull}
%%     S[{\Gamma},T,A] =
%%     \int\dn{4}{x}\Bigg[
%%       B_1\, R_{\mu\nu}{}^{\mu}{}_{\rho} T^{\nu,\alpha\beta}T^{\rho,\gamma\delta}\epsilon_{\alpha\beta\gamma\delta}
%%       +B_2\, R_{\mu\nu}{}^{\sigma}{}_\rho T^{\beta,\mu\nu}T^{\rho,\gamma\delta}\epsilon_{\sigma\beta\gamma\delta}
%%       +B_3\, R_{\mu\nu}{}^{\mu}{}_{\rho} T^{\nu,\rho\sigma}A_\sigma
